---
title: "assignment3markdown"
author: "Zaid Sameer"
date: '2018-11-01'
output: html_document
---

## Question 2

#reading the csv file

```{r}
rna_counts <- read.csv("eXpress_dm_counts.csv")
str(rna_counts)
```


checking for 0 values in rna_counts

```{r}
which(rna_counts == 0)

newrna_counts <- replace(rna_counts, rna_counts<1, 0.1)

which(newrna_counts == 0)

str(rna_counts)
str(newrna_counts)

```

```{r}

mean(rna_counts$F101_lg_female_hdhorn)
mean(newrna_counts$F101_lg_female_hdhorn)

logoffemalehdhorns <- log(newrna_counts$F101_lg_female_hdhorn, 2)
mean(logoffemalehdhorns)
mean(log(newrna_counts$F101_lg_female_hdhorn, 2))
length(logoffemalehdhorns)

#simplyfying by taking out dataframe input
# here replace newrna_counts with the dataframe of intrest

mean_col <- function( col, log2 ) {
  if (log2 == TRUE) {
    logdfrm <- log( newrna_counts[2:56], 2)
        mean( (logdfrm)[[ col ]] )
    }
  else { 
    mean( (newrna_counts)[[ col ]] )
    }
}

mean_col("F101_lg_female_hdhorn", FALSE)
mean_col("F101_lg_female_hdhorn", TRUE)
#

```

## trying another column

```{r}
mean(newrna_counts$F101_lg_female_wings)
logoffemalewings <- log(newrna_counts$F101_lg_female_wings, 2)
mean(logoffemalewings)
mean(log(newrna_counts$F101_lg_female_wings, 2))

mean_col("F101_lg_female_wings", FALSE)

mean_col("F101_lg_female_wings", TRUE)

```

## making a vector of means

```{r}

for (headername in newrna_counts[2:56]){
  print(mean(headername))
}

means_vector <- colMeans(newrna_counts[2:56])
class(means_vector)
View(means_vector)
mode(means_vector)
#or can use apply watch video (https://www.youtube.com/watch?v=7sJ8r6Lb7-o)

?colMeans
```




## draft work

# coding (here more complex because I have to input dataframe when calling the function)

mean_col <- function( dfrm, col, log2 ) {
  if (log2 == TRUE) {
    logdfrm <- log( dfrm[2:56], 2)
        mean( get(logdfrm)[[ col ]] )
    }
  else { 
    mean( get(dfrm)[[ col ]] )
    }
}

mean_col("newrna_counts", "F101_lg_female_hdhorn", TRUE)
#

mean_col("newRna_counts", "F101_lg_female_hdhorn", TRUE)
mean_col("newRna_counts", "F101_lg_female_hdhorn", FALSE)


mean()
mean(get(newRna_counts)[F101_lg_female_hdhorm])

colMeans(rna_counts)

mean_col <- function( dfrm, col ) mean( get(dfrm)[[ col ]] )

mean_col("rna_counts", "F101_lg_female_hdhorn", log= TRUE)

lognewrna_counts <- log( newrna_counts[2:56], 2)
